%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}

\setlength{\multicolsep}{-2pt}
\setlength{\columnsep}{10pt}

%----------FONT-----------
% \usepackage[sfdefault]{FiraSans}
\usepackage{charter}
%-------------------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\vspace{0pt}\scshape\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% ATS compliant
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
    \small\textbf{#1} & \small\textbf{#2} \\
  \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Prathmesh Ghatol} \\[5pt]
    \small
    \faPhone\ +91 8007700098 ~ | ~
    \href{mailto:pratham1986@gmail.com}{\faEnvelope\ pratham1986@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/prathmeshGhatol/}{\faLinkedin\ linkedin} ~ | ~
    \href{https://github.com/e-l-l}{\faGithub\ github--e-l-l} ~ | ~
    \href{https://e-l-l.github.io/portfolio-ell/}{\faGlobe\ portfolio}
\end{center}
\vspace{-12pt}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
  {Vectorshift (YC S23)}{July 2025 -- Present}
  {Software Engineer}{New York, USA}
  \resumeItemListStart
    \resumeItem{Reduced 90\% of canvas (react-flow) re-rendering issues, delivering a significantly smoother customer experience.}
    \resumeItem{Optimized data processing pipeline, reducing keystroke latency from 1000ms to 100ms (90\% improvement).}
    \resumeItem{Refactored I/O fields across the codebase, improving modularity and code reusability.}
    \resumeItem{Optimized follow-up message generation from 2s to sub-1s response times (50\%+ faster) with 80\% more relevant questions.}
    \resumeItem{Revamped and upgraded the Vectorshift browser extension with new features (Both Front and backend).}
    \resumeItem{Redesigned the platform interfaces to make them more responsive and automated, enhancing UX and platform smoothness.}
    \resumeItem{Lead frontend engineer on the Vectorshift AI Assistant feature, which helps users leverage Vectorshift more effectively.}
  \resumeItemListEnd

\resumeSubheading
  {Niti AI}{Aug 2023 -- July 2025}
  {Founding AI / ML and Software Engineer}{Bangalore, India}
  \resumeItemListStart
    \resumeItem{Boosted CTR by up to 1\% using AI-driven RAG and recommendation systems, generating 60K+ monthly clicks.}
    \resumeItem{Built super-slim platform-agnostic SDKs (React, React Native, Flutter, Android) enabling integrations in under 5 minutes.}
    \resumeItem{Developed a no-code UI editor with drag-and-drop and inline editing capabilities.}
    \resumeItem{Orchestrated AI workflows using LangGraph, FastAPI, and Next.js with human-in-the-loop logic.}
    \resumeItem{Created Growth Agents to auto-select and deploy effective growth experiences tailored to business goals.}
    \resumeItem{Built GenUI: generates frontend \& backend end-to-end user journeys from a single prompt.}
    \resumeItem{Developed Niti AI Figma plugins with a parser to convert designs into editable UI blocks on-platform.}
  \resumeItemListEnd

  \resumeSubheading
    {Think360 AI}{June 2023 -- Aug 2023}
    {Data Analyst Intern}{Mumbai, India}
    \resumeItemListStart
      \resumeItem{Built LLM-powered chatbots for support and SQL generation.}
      \resumeItem{Developed interactive HR dashboards using Power BI.}
      \resumeItem{Built fraud detection systems to flag malicious apps, enhancing client SEO.}
    \resumeItemListEnd
\resumeSubheading
  {GetWYLD}{Nov 2022 -- Dec 2022}
  {Data Analyst Intern}{Mumbai, India}
  \resumeSubheading
    {BinaryDots Fretbox}{Aug 2022 -- Nov 2022}
    {Software Engineer Intern}{Jhansi, India}
\resumeSubHeadingListEnd
\vspace{-12pt}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Uptell - Real-time Status \& Alerts Platform} $|$ \emph{Next.js, FastAPI, PostgreSQL, Supabase}}{Jun 2025}
  \resumeItemListStart
    \resumeItem{Built a multi-tenant SaaS platform with WebSocket-powered live updates, email notifications, and RBAC.}
  \resumeItemListEnd
  \resumeProjectHeading{\textbf{Lumen - Digital Transparency for Supply Chains} $|$ \emph{Next.js, Wagmi}}{Nov 2024}
  \resumeItemListStart
    \resumeItem{Won Based India 2025 Hackathon with a secure Web3 product for decentralized carbon emmision management.}
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{Car Crash \& Price Prediction} $|$ \emph{Python, Tensorflow}}{May 2023}
  \resumeItemListStart
    \resumeItem{Built deep learning pipeline to assess crash severity and predict repair costs.}
  \resumeItemListEnd

  \resumeProjectHeading{\textbf{Attendance Management System} $|$ \emph{Next.js, Node.js}}{July 2023}
  \resumeItemListStart
    \resumeItem{Built an automated attendance tracker for my college, boosting accuracy and saving approx 10\% of the lecture time.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-12pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Mumbai (DJSCE)}{Aug 2020 -- May 2024}
    {B.Tech in Information Technology (Minors - Data Science and AI/ML) \quad \textbf{\textit{CGPA: 9.1/10}}}{Mumbai, India}
\resumeSubHeadingListEnd
\vspace{-12pt}

%-----------SKILLS-----------
\section{Technical Skills}
\small
\begin{itemize}[leftmargin=*, itemsep=2pt, label={--}]
  \item \textbf{Languages}: Python, HTML/CSS, JavaScript, Typescript, Dart
  \item \textbf{Frameworks/Tools}: React, react-flow, React Native, Next.js, Flutter, FastAPI, Streamlit, LangGraph, LangChain, Figma Plugins, Telegram Bots, Discord Bots
\end{itemize}
\vspace{-12pt}


\end{document}